Logbook of corrections 2020-07-03

### 2020-10-18 docs/corrections/2020-07-03/report/report.tex
adds corrections from 2020-07-03 and updates the manuscript 2020-10-08

%*******************************************************************************
\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\graphicspath{{../}} %goes to path: docs/

\title{Recurrent Quantification Analysis of Movement Variability in Human-Humanoid Interaction Activities}
\author[1,*]{Miguel Xochicale}
\author[1]{Chris Baber}
\affil[1]{University of Birmingham, 
	School of Engineering, 
	Birmingham, 
	B15 2TT, 
	UK}
\affil[*]{map479@bham.ac.uk}

%\keywords{Keyword1, Keyword2, Keyword3}

\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}

\section*{Introduction}
Human movement requires a complex system where not only multiple
joints and limbs are involved for a specific task in a determined environment
but also perception and action of movement that affects such 
physical performance \cite{davids2003}. 
In contrast, variability in humanoid movement is usually very small,
as a result of mechanical and dynamic capabilities \cite{gouaillier2009}. 
This means that, while humanoids 
solve the degrees of freedom problem through join design and algorithms,
humans tend to have more fluid and flexible approach. Consequently, 
one can see much variability in human movement performance of even the simplest task.
Studies of human motion reveal the possibility to 
estimate features from lower dimension signals to distinguish differences between 
styles of pedalling motion \cite{Quintana-Duque2012, Quintana-Duque2016}, 
gait identification \cite{sama2013, frank2010},
and detection of pathologies \cite{gomezgarcia2014}.
The lower dimension signals from biological systems are time series 
of $1-$dimension in $\mathbb{R}$ which commonly are 
noisy, nonlinear and non-stationary \cite{gomezgarcia2014}.
Hence, nonlinear dynamics can be used to 
objectively quantify variability of lower
dimension signals \cite{Quintana-Duque2012, Quintana-Duque2016, sama2013, 
frank2010, gomezgarcia2014, marwan2011, stergiou2011}.
For instance, Bradley et al. 2015 \cite{bradley2015} reviewed methods for
nonlinear time series analysis based on the estimation of the 
embedding parameters ($m$ embedding dimension and $\tau$ embedding delay) to 
reconstruct the state space,
where an $n$-dimensional reconstructed state space using $1-$dimensional 
time series,
can preserve the topological properties of an unknown $M$-dimensional 
state space \cite{takens1981}.
Similarly, Bradley et al. 2015 \cite{bradley2015} reviewed the use of 
Recurrence Plots (RPs), a graphical representation of a two-dimensional map 
which show black and white dots as recurrences in a given $n$-dimensional system, 
and Recurrence Quantification Analysis (RQA) metrics that compute statistics in RPs.
In general, RPs and RQA provide an intuitive meaning of the time series,
for instance, RQA is quantitatively and qualitatively independent of 
embedding dimension (also verified experimentally \cite{iwanski1998}).
However, the estimation of embedding parameters and the selection of the 
right parameters to perform RQA is still an open problem.
Bradley et al. 2015 \cite{bradley2015} pointed out that
there is no general technique that can be used to compute the embedding
parameters since time series are system-dependent which means that
computing the values for embedding parameters may only work for
one purpose (e.g., prediction) and may not work well for another purpose
(e.g., computing dynamical invariants).
Additionally, methods of nonlinear dynamics for 
computing embedding parameters e.g., autocorrelation, mutual information, 
and nearest neighbour require data which is well 
sampled and with little noise \cite{garland2016}
or require signals that are purely deterministic \cite{kantz2003}.
Thus, these methods of nonlinear analysis for computing the embedding 
parameters can break down
with real-world datasets which have generally different length, 
different values of accuracy and precision (rounding errors due to finite 
precision of the measurement apparatus which include frequency 
acquisition \cite{frank2010}),
and contaminated data with different sources of noise
\cite{garland2016}.
It is then surprising that even with the previous constraints with regard to 
the quality of data, and the problem with the estimation of embedding parameters,
the use of nonlinear dynamics have proven to be helpful to understand and 
to characterise dynamics of time series 
\cite{Quintana-Duque2012, Quintana-Duque2016, sama2013, frank2010,
gomezgarcia2014, gomezgarcia2014, marwan2011, stergiou2011, bradley2015}.

@@

For this work, we are interested in exploring and investigating  
the effects of different features of time series 
(e.g. levels of smoothness, window data length,
structures of time series based on types of movements, 
types of sensors, participants and velocities) to estimate 
embedded parameters for uniform time-delay embedding, 
recurrence plots and recurrence quantification analysis.
Hence, we conducted an experiment with twenty right-handed 
healthy participants in the context of human-humanoid imitation 
activities where participants were asked to 
imitate simple arm movements performed by a humanoid robot.
The primary aim of this work is to explore the following questions:
\begin{itemize}
\item What are the effects on three nonlinear methods 
	(reconstructed state space with uniform time-delay embedding, 
	Recurrence Plots, and Recurrence Quantification Analysis), 
	for different embedding parameters, different recurrence thresholds 
	and different characteristics of time series 
	(structure of the signal, window length and smoothness of the signal)?, and 
\item What are the strengths and weaknesses of Recurrence
	Quantification Analysis for the previous conditions
	of nonlinear analysis methods?
\end{itemize}

%*******************************************************************************
%*******************************************************************************
%*******************************************************************************
\section*{Results}

@@

%*******************************************************************************
%*******************************************************************************
%*******************************************************************************
\section*{Discussion}
Time series from different sources  
(e.g., participants, movements, axis type) as well as
different characteristics (e.g., sample rate, window length or levels of smoothness) 
result in different embedding parameters and therefore different 
values for recurrence plots and recurrence quantification analysis metrics.
That said, while embedding parameters for individual
time series were successfully computed, the quantification 
of variability with regard to the shape of the trajectories in 
reconstructed state spaces require more investigation
as our initial, approach based on euclidean distances on the trajectories, 
failed to quantify trajectories which were not well unfolded. 
To then found out that Recurrence Plots along with 
Recurrence Quantification Analysis (RQA) metrics (e.g., REC, DET, RATIO and ENTR) 
and its variation of embedding parameters and recurrence thresholds 
helped to quantify the variability of different sources of time series.
However, further investigation is required to be done in order to 
have better intuition and meaningful interpretation of nonlinear 
analysis such as to find a right 
balance among (i) the level of smoothness of the signal, 
(ii) the selection of recurrence thresholds and (iii) 
the range of embedding parameters.

@@

%*******************************************************************************
%*******************************************************************************
%*******************************************************************************
\section*{Methods}
\subsection*{State Space Reconstruction}
The method of state space reconstruction \cite{packard1980} 
\cite{takens1981} has been applied in many disciplines 
\cite{aguirre2009, stergiou2011, frank2010, 
sama2013, Quintana-Duque2016}. The method of state space reconstruction is 
based on uniform time-delay embedding methodology which is a simple 
matrix implementation that can reconstruct an unknown $d-$dimensional 
manifold $M$ from a scalar time series (e.g. one-dimensional 
time series in $\mathbb{R}$). A manifold, in this context, is a 
multidimensional curved surface within a space (e.g. a saddle) 
\cite{guastello-gregson2011}.

>>>>

\documentclass[10pt]{article}
\usepackage[margin=20mm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\title{
Logbook of corrections 2020-07-03 
}
\author{Miguel Xochicale}
\date{ \today }

\begin{document}
\maketitle

\begin{abstract}
This logbook contains the suggested changes by Chris Baber 
presented in (\emph{.../corrections/2020-07-03/comments/README.md}),
fused text and further changes to the manuscript.
\end{abstract}

\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Comments}
\subsection{Text replacement}
\begin{enumerate}
\item 
"Perhaps you could replace your text with mine?  
\begin{verbatim}
Instead of replacing test, I will fuse text
\end{verbatim}
\textit{
SORTED: \\ 
Sun  4 Oct 01:11:27 BST 2020\\
}
\\
\end{enumerate}

\subsection{Experiment description}
\begin{enumerate}
\item 
"although still believe that there needs to be a bit more information in your description of the experiment, in terms of what participants had to do and in terms of the data collection"
\begin{verbatim}

Comestic changes changes to the experiment sections were made.
These include the subsections of particianpts, ethics, hhi activiites,
data collection from imus, raw data, data normalization smoothing, windowding

\end{verbatim}
\textit{
SORTED: \\ 
Sun 18 Oct 04:19:38 BST 2020
\\
}
\\
\end{enumerate}

\section{Introduction}

\subsection{ORIGINAL TEXT}
\begin{verbatim}
\section*{Introduction}
Human movement requires a complex system where not only multiple
joints and limbs are involved for a specific task in a determined environment
but also perception and action of movement that affects such 
physical performance \cite{davids2003}. 
In contrast, variability in humanoid movement is usually very small,
as a result of mechanical and dynamic capabilities \cite{gouaillier2009}. 
This means that, while humanoids 
solve the degrees of freedom problem through join design and algorithms,
humans tend to have more fluid and flexible approach. Consequently, 
one can see much variability in human movement performance of even the simplest task.
Studies of human motion reveal the possibility to 
estimate features from lower dimension signals to distinguish differences between 
styles of pedalling motion \cite{Quintana-Duque2012, Quintana-Duque2016}, 
gait identification \cite{sama2013, frank2010},
and detection of pathologies \cite{gomezgarcia2014}.
The lower dimension signals from biological systems are time series 
of $1-$dimension in $\mathbb{R}$ which commonly are 
noisy, nonlinear and non-stationary \cite{gomezgarcia2014}.
Hence, nonlinear dynamics can be used to 
objectively quantify variability of lower
dimension signals \cite{Quintana-Duque2012, Quintana-Duque2016, sama2013, 
frank2010, gomezgarcia2014, marwan2011, stergiou2011}.
For instance, Bradley et al. 2015 \cite{bradley2015} reviewed methods for
nonlinear time series analysis based on the estimation of the 
embedding parameters ($m$ embedding dimension and $\tau$ embedding delay) to 
reconstruct the state space,
where an $n$-dimensional reconstructed state space using $1-$dimensional 
time series,
can preserve the topological properties of an unknown $M$-dimensional 
state space \cite{takens1981}.
Similarly, Bradley et al. 2015 \cite{bradley2015} reviewed the use of 
Recurrence Plots (RPs), a graphical representation of a two-dimensional map 
which show black and white dots as recurrences in a given $n$-dimensional system, 
and Recurrence Quantification Analysis (RQA) metrics that compute statistics in RPs.
In general, RPs and RQA provide an intuitive meaning of the time series,
for instance, RQA is quantitatively and qualitatively independent of 
embedding dimension (also verified experimentally \cite{iwanski1998}).
However, the estimation of embedding parameters and the selection of the 
right parameters to perform RQA is still an open problem.
Bradley et al. 2015 \cite{bradley2015} pointed out that
there is no general technique that can be used to compute the embedding
parameters since time series are system-dependent which means that
computing the values for embedding parameters may only work for
one purpose (e.g., prediction) and may not work well for another purpose
(e.g., computing dynamical invariants).
Additionally, methods of nonlinear dynamics for 
computing embedding parameters e.g., autocorrelation, mutual information, 
and nearest neighbour require data which is well 
sampled and with little noise \cite{garland2016}
or require signals that are purely deterministic \cite{kantz2003}.
Thus, these methods of nonlinear analysis for computing the embedding 
parameters can break down
with real-world datasets which have generally different length, 
different values of accuracy and precision (rounding errors due to finite 
precision of the measurement apparatus which include frequency 
acquisition \cite{frank2010}),
and contaminated data with different sources of noise
\cite{garland2016}.
It is then surprising that even with the previous constraints with regard to 
the quality of data, and the problem with the estimation of embedding parameters,
the use of nonlinear dynamics have proven to be helpful to understand and 
to characterise dynamics of time series 
\cite{Quintana-Duque2012, Quintana-Duque2016, sama2013, frank2010,
gomezgarcia2014, gomezgarcia2014, marwan2011, stergiou2011, bradley2015}.

@@

For this work, we are interested in exploring and investigating  
the effects of different features of time series 
(e.g. levels of smoothness, window data length,
structures of time series based on types of movements, 
types of sensors, participants and velocities) to estimate 
embedded parameters for uniform time-delay embedding, 
recurrence plots and recurrence quantification analysis.
Hence, we conducted an experiment with twenty right-handed 
healthy participants in the context of human-humanoid imitation 
activities where participants were asked to 
imitate simple arm movements performed by a humanoid robot.
The primary aim of this work is to explore the following questions:
\begin{itemize}
\item What are the effects on three nonlinear methods 
	(reconstructed state space with uniform time-delay embedding, 
	Recurrence Plots, and Recurrence Quantification Analysis), 
	for different embedding parameters, different recurrence thresholds 
	and different characteristics of time series 
	(structure of the signal, window length and smoothness of the signal)?, and 
\item What are the strengths and weaknesses of Recurrence
	Quantification Analysis for the previous conditions
	of nonlinear analysis methods?

\end{verbatim}

\subsection{SUGGESTED TEXT}
\begin{verbatim}
The complexity of human movement arises from the balancing of consistency 
and variability in solving the Degrees of Freedom problem (Bernstein, xx). 
Each joint can be moved in more than one plane, leading to many possible 
combinations which need to be reduced into order to perform a control action (Newell, xx). 
However, too much reduction can result in highly consistent movement which lacks 
sufficient variability to allow adaptation to situational demands. 
Consequently, one can see much variability in human movement even the 
simplest of movements.  Variability can be beneficial in supporting adaptability 
and can reflect experience and expertise of the performance, e.g., in cycling.  
Uncontrolled variability, due to disease, disfunction or inexperience, 
can be detrimental to performance and plays a role in detection of pathologies. 
While the analysis of movement of variability is becoming increasingly 
popular as a diagnostic tool, there remain challenges in terms of defining 
the most appropriate methods and parameters to apply. In part, 
these challenges stem from the fact that the identification movement 
variability requires analysis of signals which are time-series of 1-dimension 
in R which are noisy, nonlinear and non-stationary.  
Further problems arise from assigning a plausible locus of control to 
the movements, e.g., in order to determine whether variability is the 
result of deliberative control by the performer or whether it arises 
from exogenous or endogenous disturbances.  For this paper, our focus 
is on the analysis of signals; specifically, in terms of objectively 
quantifying variability of lower dimension signals using time-series analysis.

Methods for time-series analysis generally involve the estimation 
of embedding parameters (m embedding dimension and T embedding delay) 
which are used to reconstruct the n-dimensional state space of 
the 1-dimension time-series.  Key to the selection of these 
parameters is the need to ensure that the topological properties 
of the (unknown) M-dimensional state space.   A popular approach 
to the construction of these state spaces involves the use of 
Recurrence Plots (RPs) which provide a graphical two-dimensional 
map (using black and white dots) to indicate recurring patterns 
in the n-dimensional system.  While RPs provide a human 
interpretable picture of the system, these require further 
analysis to allow the properties of that system to be quantified, 
and so Recurrence Quantification Analysis (RQA) can be applied.  
However, the estimation of the embedding parameters for 
RQA remains an open problem (Bradley et al., 2015).

There is no agreed method for estimating embedding parameters 
(for RQA or for other nonlinear analysis methods) because time-series 
are system-dependent, i.e., these rely on the initial conditions, 
and on the configuration and behaviour of the system.  
This means that, unless one holds all of the influencing 
variables constant, embedding parameters computed for one 
instance may not apply to another instance.   
One could apply methods, such as autocorrelation, mutual information, 
nearest neighbour (and we will apply these in this paper), 
but these methods assume that the data are well sampled, with 
little noise and (usually) that the signals are purely deterministic.  
As such, these methods can break-down in the face of real-world datasets 
which could have different length, different degrees of precision, or 
different levels of contamination from exogenous and endogenous 
sources of ‘noise’.  What is, perhaps, surprising is that 
even subject to these problems, the methods are useful and 
nonlinear dynamics approaches continue to tell us much about 
human movement.

For this paper, we explore the role of RP and RQA in the 
analysis of simple human movement.  We compare horizontal and 
vertical arm movements performed by neurotypical participants 
who are copying these movements being made by a humanoid robot.  
This provides an initial point of comparison 
(between human movement, which we assume to have a degree of variability, 
and the robot, which we assume to have a degree of consistency).   
Additionally, our interest lies in the estimation of embedding parameters 
in light of different features of the data, e.g., levels of smoothing, 
window length, structure of time-series based on movement, 
types of sensors, individual differences between participants and 
the movements that they perform. Specifically, we ask what are 
the effects of different embedding parameters, recurrence thresholds 
and characteristics of time-series on nonlinear analysis 
methods (i.e., reconstructed state space with 
uniform time-delay embedding, Recurrence Plots and 
Recurrence Quantification Analysis)?

\end{verbatim}

\subsection{FUSED TEXT}
\begin{verbatim}

\section*{Introduction}
The complexity of human movement arises from the process of mastering 
redundant (bio)mechanical degrees of freedom (DOF) to successfully 
accomplish any given motor task (Bernstein, 1967).
Such DOF are independent coordinates to uniquely 
describe the configuartions of the system which provides flexibiity 
and stability to adapt to a change enviroment conditions but 
that leads many possible combinations (Newell and Vaillancourt, 2001).
Hence, human movement complexity can be seen as a balance 
between the required DOF "to generate a stable (persistent) 
and flexible (variable) behavioural output in response to 
changing intentions and dynamic environmental
conditions" \cite{davids2003}. 
Consequently, one can see much variability in human movement even the 
simplest of movements.  
While the analysis of movement of variability is becoming increasingly 
popular as a diagnostic tool or skill performance evaluation, 
there remain challenges in terms of defining 
the most appropriate methods and parameters to apply. 
In part, 
these challenges stem from the fact that the identification movement 
variability requires analysis of signals which are time-series of 
of $1-$dimension in $\mathbb{R}$ which are 
noisy, nonlinear and non-stationary \cite{gomezgarcia2014}.
Further problems arise from assigning a plausible locus of control to 
the movements, e.g., in order to determine whether variability is the 
result of deliberative control by the performer or whether it arises 
from exogenous or endogenous disturbances.  For this paper, our focus 
is on the analysis of signals; specifically, in terms of objectively 
quantifying variability of lower dimension signals using time-series analysis.

Methods for nonlinear time series analysis generally involve the estimation of the 
embedding parameters ($m$ embedding dimension and $\tau$ embedding delay) to 
reconstruct the state space,
where an $n$-dimensional is reconstructed state space using $1-$dimensional 
time series \cite{Quintana-Duque2012, Quintana-Duque2016, sama2013, 
frank2010, gomezgarcia2014, marwan2011, stergiou2011}.
Key to the selection of these parameters is the need to preserve 
topological properties of an unknown $M$-dimensional state space \cite{takens1981}.
An common approach to the construction of these state spaces 
involves Recurrence Plots (RPs), a graphical representation of black and white dots, 
which shows recurrent patterns of a $n$-dimensional system.
While RPs provide a human
interpretable picture of the system, these require further
analysis to allow the properties of that system to be quantified,
and so Recurrence Quantification Analysis (RQA) can be applied.
However, the estimation of the embedding parameters for
RQA remains an open problem (Bradley et al. 2015 \cite{bradley2015})
There is no agreed method to estimate embedding parameters
for RQA and other nonlinear methods \cite{bradley2015} 
because time series are system-dependent, i.e., these rely
on the initial conditions, and on the configuration and behaviour of the system.  
This means that, unless one holds all of the influencing 
variables constant, embedding parameters computed for one 
instance may not apply to another instance.

One could apply methods, such as autocorrelation, mutual information, 
nearest neighbour (and we will apply these in this paper), 
but these methods assume that the data are well sampled, with 
little noise and (usually) that the signals are purely deterministic \cite{garland2016, kantz2003}.
That said, these methods can break-down in the face of real-world datasets 
which could have 
different length, 
different values of accuracy and precision (rounding errors due to finite 
precision of the measurement apparatus which include frequency 
acquisition \cite{frank2010}), or 
different levels of contamination from exogenous and endogenous 
sources of ‘noise’ \cite{garland2016}.  What is, perhaps, surprising is that 
even subject to these problems, the methods are useful and 
nonlinear dynamics approaches continue to tell us much about 
human movement \cite{Quintana-Duque2012, Quintana-Duque2016, sama2013, frank2010,
gomezgarcia2014, marwan2011, stergiou2011, bradley2015}.

For this paper, we explore the role of RPs and RQA in the 
analysis of simple human movement. 
We compare horizontal and 
vertical arm movements performed by neurotypical participants 
who are copying these movements being made by a humanoid robot.  
This provides an initial point of comparison 
(between human movement, which we assume to have a degree of variability, 
and the robot, which we assume to have a degree of consistency).   
Additionally, our interest lies in the estimation of embedding parameters 
in light of different features of the data, e.g., levels of smoothing, 
window length, structure of time-series based on movement, 
types of sensors, individual differences between participants and 
the movements that they perform. 
Specifically, we ask what are 
the effects of different embedding parameters, recurrence thresholds 
and characteristics of time-series on nonlinear analysis 
methods (i.e., reconstructed state space with 
uniform time-delay embedding, RPs and RQA)?

\end{verbatim}

\textit{
SORTED: \\ 
Tue 11 Aug 18:37:21 BST 2020 \\
Sun 18 Oct 04:27:51 BST 2020
\\
}

\section{Results}
\subsection{ORIGINAL TEXT}
\begin{verbatim}

\section*{Results}

@@

\end{verbatim}

\subsection{SUGGESTED TEXT}
\begin{verbatim}

Reconstructed State Spaces
As noted in the Introduction, a challenge in the implantation of uniform time-delay embedding 
arises from the selection of embedding parameters because of the uniqueness of each time series 
in terms of its structure (e.g., modulation of amplitude, frequency, phase etc.). 
With that in mind, the options are to either calculate embedding parameters for each unique 
instance (which can make comparison challenging) or to find parameters which can apply to all 
instances in the study.  We recognise that the latter approach is not without its problems, 
but our approach is to compute sample mean over all values in each of the conditions of the 
time series for minimum dimension and minimum delay values.

Minimum embedding parameters
Minimum embedding parameters were initially computed using False Nearest Neighbour (FNN) 
and Average Mutual Information (AMI).   We used FNN to calculate a value for m 
and AMI to calculate a value for X? Comment: You should provide a sentence here 
to justify the use these different methods for m and X? 
To illustrate this, figure (A) show box plots for minimum embedding values for sensors 
on the wrist of the human (HS01) and the robot (RS01).   
As we had assumed, minimum embedding values for HS01 show greater variation than 
those for RS01 (as indicated by differences in interquartile ranges).  
Additionally, figure (A) show a decrease in mean values (rhombus) in the box plots 
as smoothness of the time-series increases (see sg0, sg1, sg2).  
Figure (B) show box plots for Average Mutual Information (AMI).  
One can see that, in contrast to RS01, minimum values for HS01 tend to spread 
as the smoothness of the time-series increases.
The sample mean for minimum value of embedding parameter, m derived from 
FNN  (figures A) is 6 and  Tfrom AMI (figures B) is 8.

Uniform Time-delay embedding
Using the minimum embedding parameters (defined above), 
the first three axis of the rotated Principal Components Analysis (PCA) 
are shown for the reconstructed state spaces of horizontal (figures  ) 
and vertical (figures ) arm movements.   While visual inspection of these figures 
suggests differences in the trajectories of the reconstructed state spaces, 
we require an objective quantification to determine the extent of the differences.  
One approach could be use Euclidean distances from the origin for points in these 
trajectories, but this proved inconclusive and was not able to capture 
the dynamics of the trajectories. Consequently, we applied RP and RQA.

Recurrence Plots
Using the minimum embedding parameters and a recurrence threshold of 1 
Comment: you should explain why you chose 1 here Recurrence Plots (RP) were 
computed for horizontal (figures ) and vertical (figures ) arm movements.

Recurrence Quantification Analysis
Four Recurrence Quantification Analysis metrics (percentage recurrence, REC, 
representing the percentage of black dots in RP; percentage determinism, DET, 
representing the predictability of the RP; ratio of DET / REC, RATIO; 
Shannon entropy, ENTR) were computed using the same parameters as for RP.

REC values
Figure (A) presents box plots of REC which show that REC values, 
for HS01, are more spread for Slow (i.e., 5 seconds per movement) movements 
in Horizontal (HS) or Vertical (VS) than for Fast (i.e., 2 seconds per movement).  
This suggests greater variation between participants for the Slow movements.  
For RS01, there is little variation between Slow and Fast movement.  
In terms of smoothness, there seems little effect of HS01 but RS01 values 
do show affects of smoothness.

DET values
Figure (b) presents DET values and shows little difference for type of movement or performer.  
However, DET values are affected by changes in smoothness of the signal, 
particularly for Fast movement.

RATIO values
Figure (C) presents the ratio of DET / REC.  These values, for the human performer, 
vary less for HN than for HF movement.  
Additionally, smoothness leads to a decrease in mean values for Fast movements.

ENTR values
Figure (d) shows ENTR values are higher for the human performer than the robot, 
and vary with the smoothness of the time-series.

3D RQA ENTR
As ENTR appeared to be have higher sensitivity than the other measures, 
we explored the impact of different embedding parameters /{m.../}, /{.../} 
incrementing by 1 each run, with recurrence thresholds e = 1,2,3 and levels of 
smoothness (sg0, sg1, sg2).  
Figure ( ) shows that increasing recurrence 
threshold leads to an increase in ENTR regardless of level of smoothness.  
Increasing level of smoothness will also increase ENTR (figure () ).  
In terms of movement or performer, RQA ENTR decrease from Slow (HS, VS) to Fast (HF, VF) 
for both human and robot.   In terms of individual differences, for human participants, 
figure ( ) compares p01, p02 and p03 (for illustrative purposes) – 
both between each other and in comparison with the more consistent performance of the robot.  
In terms of window length (w100 (2s), w250 (5s), w500(10s), w750 (15s)), figure ( ) 
shows that improvement in capture with number of samples, although this has less 
of an effect on RQA ENTR.

\end{verbatim}

\subsection{FUSED TEXT}
\begin{verbatim}

%*******************************************************************************
%*******************************************************************************
\section*{Results}

\subsection*{Reconstructed State Spaces}
As noted in the Introduction, a challenge in the implementation of uniform time-delay embedding 
arises from the selection of embedding parameters because of the uniqueness of each time series 
in terms of its structure (e.g., modulation of amplitude, frequency, phase etc.). 
With that in mind, the options are to either calculate embedding parameters for each unique 
instance (which can make comparison challenging) or to find parameters which can apply to all 
instances in the study.
We recognise that the latter approach is not without its problems, 
but our approach is to compute sample mean over all values in each of the conditions of the 
time series for minimum dimension and minimum delay values.

\subsubsection*{Minimum embedding parameters}
Minimum embedding parameters were initially computed using False Nearest Neighbour (FNN) 
and Average Mutual Information (AMI).   We used FNN to calculate a value for $m$
to unfold the attractors and AMI to calculate a value for $\tau$ and maxime the 
information in the unfolded attractor.
To illustrate this, figure \ref{fig:cao_ami} (A) show box plots for minimum embedding 
values for sensors on the wrist of the human (HS01) and the robot (RS01).   
As we had assumed, minimum embedding values for HS01 show greater variation than 
those for RS01 (as indicated by differences in interquartile ranges).  
Additionally, figure \ref{fig:cao_ami} (A) show a decrease in mean values (rhombus) in the box plots 
as smoothness of the time-series increases (see sg0, sg1, sg2).  
Figure \ref{fig:cao_ami} (B) show box plots for Average Mutual Information (AMI).  
One can see that, in contrast to RS01, minimum values for HS01 tend to spread 
as the smoothness of the time-series increases.
The sample mean for minimum value of embedding parameter, 
$m$ derived from FNN  (figures \ref{fig:cao_ami} A) is $\overline{m}_0=6$ 
and $\tau$ from AMI (figures \ref{fig:cao_ami} B) is $\overline{\tau}_0=8$.

%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/caoami/pdf/fig2}
	\caption{
	{\bf Box plots of minimum embedding parameters.} 
	Box plots of (A) minimum embedding dimensions 
	and (B) first minimum AMI values for 
	Horizontal Normal (HN), Horizontal Faster (HF),
	Vertical Normal (VN) and Vertical Faster (VF)
	with sensors attached to participants (HS01) and
	sensor attached to robot (RS01).
	Minimum embedding parameters are for twenty participants 
	($p01$ to $p20$) with three smoothed signals 
	(sg0: sg0zmuvGyroZ, sg1: sg1zmuvGyroZ and sg2: sg2zmuvGyroZ)
	and window length of 10-sec (500 samples).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig:cao_ami}
\end{figure}
%%---------------------------------(FIGURE)------------------------------------

\subsubsection*{Uniform Time-Delay Embedding}
Using the overall embedding parameters ($\overline{m_0}=6$, $\overline{\tau_0}=8$), 
the first three axis of the rotated Principal Components Analysis (PCA) 
are shown for the reconstructed state spaces of horizontal (figures~\ref{fig:rss_aHw10}) 
and vertical (figures~\ref{fig:rss_aVw10}) arm movements. 
While visual inspection of these figures 
suggests differences in the trajectories of the reconstructed state spaces, 
we require an objective quantification to determine the extent of the differences.  
One approach could be use Euclidean distances from the origin for points in these 
trajectories, but this proved inconclusive and was not able to capture 
the dynamics of the trajectories. Consequently, we applied 
Recurrence Plots and Recurrence Quantification Analysis.

\subsection*{Recurrences Plots}
Using the average embedding parameters 
($\overline{m}_0=6$, $\overline{\tau}_0=8$) 
and an recurrence threshold of $\epsilon=1$.
As our interest is for dynamical transitions, 
there is little importance on the selection of $\epsilon$ which in this case
is 1. 
Recurrence Plots (RP) were computed for horizontal (figures~\ref{fig:rp_aH}) and 
vertical (figures~\ref{fig:rp_aV}) arm movements.

\subsection*{Recurrence Quantification Analysis} \label{ch6:rqas}
Four Recurrence Quantification Analysis metrics (
percentage recurrence, REC, representing the percentage of black dots in RP; 
percentage determinism, DET, representing the predictability of the RP; 
ratio of DET / REC, RATIO; Shannon entropy, ENTR) 
were computed using the same parameters as for RP.
%\subsubsection*{REC values}
Figure~\ref{fig:RQABP}(A) presents box plots of REC values, 
for HS01, are more spread for Slow (i.e., 5 seconds per movement) movements 
in Horizontal (HS) or Vertical (VS) than for Fast (i.e., 2 seconds per movement).  
This suggests greater variation between participants for the Slow movements.  
For RS01, there is little variation between Slow and Fast movement
(interquartile range of 0.01). 
In terms of smoothness, there seems little effect of HS01 but RS01 values 
do show affects of smoothness (see the incremental changes of mean values (rhombus)).
%\subsubsection*{DET values}
Figure \ref{fig:RQABP}(B) presents DET values and shows 
little difference for type of movement or performer.  
However, DET values are affected by changes in smoothness of the signal, 
particularly for Fast movement.
%\subsubsection*{RATIO values}
Figure \ref{fig:RQABP}(C) presents the ratio of DET / REC. 
These values, for the human performer, vary less for HN than for HF movement.  
Additionally, smoothness leads to a decrease in mean values for Fast movements.
%\subsubsection*{ENTR values}
Figure \ref{fig:RQABP}(D) shows ENTR values are higher for the human 
performer than the robot, and vary with the smoothness of the time-series.

\subsection*{3D RQA ENTR}
As ENTR appeared to be have higher sensitivity than the other measures, 
we explored the impact of different embedding parameters 
$ \{ m \in \mathbb{R} | 1 \le m \le 10  \} $,
$  \{ \tau \in \mathbb{R} | 1 \le \tau \le 10  \} $ 
incrementing by 1 each run, with recurrence thresholds $\epsilon=1, 2, 3$ 
and levels of smoothness (sg0, sg1, sg2).  
Figure \ref{fig:RQA-IND} shows that increasing recurrence 
threshold leads to an increase in ENTR regardless of level of smoothness.  
Similarly, increasing level of smoothness will also increase ENTR (figure \ref{fig:RQA-IND}).
In terms of movement or performer, RQA ENTR decrease from Slow (HS, VS) to Fast (HF, VF) 
for both human (HS01) and (RS01) (Figures~\ref{fig:3dRQAENTR_sensoractivities}).
In terms of individual differences, for human participants, 
figure \ref{fig:3dRQAENTR_participantsactivities} compares p01, p02 and p03 (for illustrative purposes) --
both between each other and in comparison with the more consistent performance of the robot.  
In terms of window length (w100 (2s), w250 (5s), w500(10s), w750 (15s)), 
figure \ref{fig:3dRQAENTR_windowsactivities} shows that improvement in 
capture with number of samples, although this has less of an effect on RQA ENTR.

\end{verbatim}

\textit{
SORTED: \\ 
Tue  1 Sep 23:43:03 BST 2020\\
Sat  3 Oct 14:54:05 BST 2020\\
Sat  3 Oct 23:55:12 BST 2020 \\
}
\\

\section{Discussion}

\subsection{ORIGINAL TEXT}
\begin{verbatim}

\section*{Discussion}
Time series from different sources  
(e.g., participants, movements, axis type) as well as
different characteristics (e.g., sample rate, window length or levels of smoothness) 
result in different embedding parameters and therefore different 
values for recurrence plots and recurrence quantification analysis metrics.
That said, while embedding parameters for individual
time series were successfully computed, the quantification 
of variability with regard to the shape of the trajectories in 
reconstructed state spaces require more investigation
as our initial, approach based on euclidean distances on the trajectories, 
failed to quantify trajectories which were not well unfolded. 
To then found out that Recurrence Plots along with 
Recurrence Quantification Analysis (RQA) metrics (e.g., REC, DET, RATIO and ENTR) 
and its variation of embedding parameters and recurrence thresholds 
helped to quantify the variability of different sources of time series.
However, further investigation is required to be done in order to 
have better intuition and meaningful interpretation of nonlinear 
analysis such as to find a right 
balance among (i) the level of smoothness of the signal, 
(ii) the selection of recurrence thresholds and (iii) 
the range of embedding parameters.

\end{verbatim}

\subsection{SUGGESTED TEXT}
\begin{verbatim}

While there are many approaches to estimating embedding parameters for nonlinear analysis, 
these can be influenced by the structure of the time-series data.   
We show that, for RSS, RP and RQA, the estimation of embedding parameters can be performed 
using a sample mean which, together with recurrence threshold, can be shown to be 
influenced by activity, performer, window length and smoothness of time-series.  
It is known that time-series from different sources and with different characteristics 
require different embedding parameters, and this can produce different RPs.  
We have shown how RQA metrics can help to quantify movement variability.

\end{verbatim}

\subsection{FUSED TEXT}
\begin{verbatim}

\section*{Discussion}
While there are many approaches to estimating embedding parameters for nonlinear analysis, 
these can be influenced by the structure of the time-series data.   
We show that, for RSS, RP and RQA, the estimation of embedding parameters can be performed 
using a sample mean which, together with recurrence threshold, can be shown to be 
influenced by activity, performer, window length and smoothness of time-series.  
It is known that time-series from different sources and with different characteristics 
require different embedding parameters, and this can produce different RSS, RPs and RQAs. 
Although this work helps to understand the open problem of 
finding right balance among (i) the level of smoothness of the signal, 
(ii) the selection of recurrence thresholds and (iii) 
the range of embedding parameters, 
we have shown how RQA metrics can help to quantify movement variability.

\end{verbatim}

\textit{
SORTED: \\ 
Sun  4 Oct 00:52:04 BST 2020\\
}
\\

\section{Conclusions}

\subsection{ORIGINAL TEXT}
\begin{verbatim}

@@

\end{verbatim}
